---
layout:  post
title: "RMarkdown Sample Post"
output:
  html_document:
    mathjax:  default
    fig_caption:  true
---

Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. Sample post. 

```{r include = FALSE}
library(knitr)
```

Run code, show output:

```{r}
summary(cars)
```

Embed plots:

```{r, echo=FALSE}
plot(cars)
```

<p class = "figcaption">Here is a plot for you.</p>

Inline math:  $$ \pi/2 \approx 1.57 $$. 

Displayed math:

$$ \sum_{i=1}^{n} i = \frac{n(n+1)}{2}.$$